The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-15 src/ms.tex

In addition to the two grants described above, the project benefited from
a Gemini Observatory contract under its Science User Support Department,
which awarded funds for development work that supports both the Astropy and
DRAGONS projects. The project also received financial support from the Dunlap
Seed Funding program at the University of Toronto to develop educational
resources for scientific software packaging within the Learn Astropy
framework.  The project also indirectly benefited from the NRAO ALMA Development
Study program, which supported the grant ``Linking CASA to the astropy ecosystem''\foontnote{\url{https://science.nrao.edu/facilities/alma/science_sustainability/Spectral_Cube_and_Radio_Beam_Ginsburg.pdf}}.
All of these successful proposals show that the Astropy Project
is vital for the astronomical infrastructure and community at large, and
strengthen its promising and sustainable future.

>>>>

In addition to the two grants described above, the project benefited from
a Gemini Observatory contract under its Science User Support Department,
which awarded funds for development work that supports both the Astropy and
DRAGONS projects. The project also received financial support from the Dunlap
Seed Funding program at the University of Toronto to develop educational
resources for scientific software packaging within the Learn Astropy
framework.  The project also indirectly benefited from the NRAO ALMA Development
Study program, which supported the grant ``Linking CASA to the astropy ecosystem''\footnote{\url{https://science.nrao.edu/facilities/alma/science_sustainability/Spectral_Cube_and_Radio_Beam_Ginsburg.pdf}}.
All of these successful proposals show that the Astropy Project
is vital for the astronomical infrastructure and community at large, and
strengthen its promising and sustainable future.
